\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\definecolor{mutedgray}{RGB}{200, 200, 200}

\pagestyle{empty}
\thispagestyle{empty}
\urlstyle{same}

\titleformat{\section}{\large\bfseries\scshape}{}{0em}{}[{\color{mutedgray}\titlerule}]
\titlespacing*{\section}{0pt}{7pt}{4pt}

\newcommand{\resumeItem}[1]{
  \item\small{#1\vspace{-2pt}}
}

\usepackage{color}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=black
}

\begin{document}

%----------------------------------------------------------------------------------------
%	3-COLUMN TOP HEADER STRUCTURE
%----------------------------------------------------------------------------------------
\noindent
\begin{minipage}[t]{0.25\textwidth}
    \small 
    \flushleft
    333 Sunol St, \\
    \vspace{2pt}
    San Jose, CA 95126 
\end{minipage}
\begin{minipage}[t]{0.50\textwidth}
    \centering
    {\Huge \textbf{Abhijeet Padwal}} \\ \vspace{6pt} 
    \small 
    \href{https://github.com/padwalab}{github.com/padwalab} $\cdot$ \href{https://linkedin.com/in/abhijeetpadwal}{linkedin.com/in/abhijeetpadwal}
\end{minipage}
\begin{minipage}[t]{0.25\textwidth}
    \small 
    \flushright
    +1 (408) 207-8784 \\
    \vspace{2pt}
    \href{mailto:padwalab@gmail.com}{padwalab@gmail.com}
\end{minipage}

\vspace{10pt}

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Go, Java, Python, JavaScript, Shell Scripting (Bash), SQL} \\
     \textbf{Distributed Systems}{: Kafka, Flink, Beam, Spark, Stream Processing, Big Data Analytics} \\
     \textbf{Databases \& Storage}{: PostgreSQL, MongoDB, Redis, Pinot, Kusto, Azure MDM, HDFS, Hive, Trino} \\
     \textbf{Tools \& Technologies}{: Docker, Kubernetes, Grafana, Grafana plugins, OpenTelemetry, FluentBit}
    }}
\end{itemize}
\vspace{-5pt}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Experience}
\begin{itemize}[leftmargin=0.15in, label={}]

    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{LinkedIn} & Sunnyvale, CA \\
      \textit{Sr. Software Engineer (Member Observability Data Platform)} & Jan 2022 -- Present \\
    \end{tabular*}\vspace{-5pt}
    \begin{itemize}[leftmargin=0.15in, topsep=2pt, itemsep=2pt]
        \resumeItem{Accelerated processing speeds by leading the migration of crash reporting and site speed pipelines, reducing crash metric latency from 15 minutes to 1 minute and site speed processing from 1 day to 1 minute.}
        \resumeItem{Built foundational streaming components including Kafka event processing, dimension extraction, event throttling, validation, and metric extraction to enable reusable, real-time processing of observability data.}
        \resumeItem{Engineered real-time crash pipelines streaming $\sim$500M web/mobile error events daily, conducting stacktrace unminification and symbolication with automated exception ticketing and dark canary validation.}
        \resumeItem{Designed and operationalized an automated site speed regression detection system for 10+ workflows processing $\sim$10 TB/day of telemetry, cutting manual pipeline interventions by 90\% via automated backfill handling and ticket resolution.}
        \resumeItem{Integrated performance metrics directly into the A/B testing experimentation platform, making regressions an automated blocker for build ramps and successfully preventing $\sim$200 regressions over 6 months.}
        \resumeItem{Operationalized metrics by building Grafana dashboards on top of the MDM metric data store, driving down reporting delays and reducing custom alerting time-to-detection to 30 minutes.}
        \resumeItem{Collaborated with the Abuse security team to implement bot and scraper traffic filters, significantly reducing false-positive regressions and maximizing signal-to-noise across performance alerts.}
    \end{itemize}

    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{TIBCO Software Inc.} & Pune, MH, India \\
      \textit{AMTS, QA} & July 2018 -- Dec 2021 \\
    \end{tabular*}\vspace{-5pt}
    \begin{itemize}[leftmargin=0.15in, topsep=2pt, itemsep=2pt]
        \resumeItem{Optimized legacy automation runtime and resolved critical Java heap space and garbage collection bottlenecks by modifying internal test framework configuration build files and jars.}
        \resumeItem{Validated robust REST-JSON plugin features for the BW5 platform and orchestrated validation workflows for MongoDB plugins deployed on BW6.}
        \resumeItem{Configured and evaluated distributed Apache Hadoop clusters and containerized applications using Docker to validate big data plugin extensions.}
    \end{itemize}

\end{itemize}
\vspace{-10pt}

%----------------------------------------------------------------------------------------
%	ACADEMIC PROJECTS
%----------------------------------------------------------------------------------------
\section{Academic Projects}
\begin{itemize}[leftmargin=0.15in, label={}]
    
    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{BitCorner (Bitcoin Exchange Platform)} $|$ \textit{\small{Java, Spring Boot, React, Redux, PostgreSQL}} & Apr 2021 -- May 2021 \\
    \end{tabular*}\vspace{-5pt}
    \begin{itemize}[leftmargin=0.15in, topsep=2pt, itemsep=2pt]
        \resumeItem{Engineered a fair order execution matching algorithm to process real-time market and limit price transaction requests for cryptocurrency exchange.}
        \resumeItem{Designed and deployed a microservices-based system architecture to AWS, integrating localized billing and multi-currency exchange handling via JPA ORM.}
    \end{itemize}

    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{eDiligence (Containerized Infrastructure Platform)} $|$ \textit{\small{Go, Nginx, Docker, GitHub Actions}} & Aug 2020 -- Dec 2020 \\
    \end{tabular*}\vspace{-5pt}
    \begin{itemize}[leftmargin=0.15in, topsep=2pt, itemsep=2pt]
        \resumeItem{Architected a scalable, microservices-oriented backend structure from scratch using Go, optimizing resource allocation to minimize infrastructure deployment costs on DigitalOcean.}
        \resumeItem{Implemented an Nginx API Gateway alongside continuous integration pipelines (GitHub Actions) integrated with a validation test framework to accelerate artifact build-and-release cycles.}
    \end{itemize}

    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{Full-Stack Application Clones} $|$ \textit{\small{Reddit, Splitwise}} & \\
    \end{tabular*}\vspace{-5pt}
    \begin{itemize}[leftmargin=0.15in, topsep=2pt, itemsep=2pt]
        \resumeItem{Developed full-stack web application clones of Reddit and Splitwise to master advanced state management, relational schema modeling, and complex business logic implementation.}
    \end{itemize}

\end{itemize}
\vspace{-10pt}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{itemize}[leftmargin=0.15in, label={}]
    
    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{San Jose State University} & San Jose, CA \\
      \textit{Master of Science in Computer Software Engineering} & Aug 2020 -- May 2022 \\
    \end{tabular*}\vspace{-5pt}
    \begin{itemize}[leftmargin=0.15in, topsep=2pt, itemsep=2pt]
        \resumeItem{\textbf{Coursework:} Software Security, Big Data Engineering, Systems Engineering, Distributed Systems, Enterprise Application Development, Data Mining, Advanced Parallel Systems.}
    \end{itemize}

\end{itemize}

\end{document}
